\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and a Multi-Armed Bandit Model with Correlated Rewards to Accelerate Robust Grasp Planning \versionline{9}

### 2015-09-15 ICRA2016/bandits_docs/includes/experiments.tex
First 8 page version ready with fb from Mel and Mathieu as well

The bandwidths of our similarity kernel were constrained to be diagonal for the grasp parameters features $C_g = \Lambda$, isotropic for the global shape features $C_s = \sigma I$ for $\sigma \in \bR$, and a Gaussian mask $C_d$ centered on the differential heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
The bandwidths were selected by maximizing the log likelihood of the true $P_F$ under the CCBP model on the validation set using a grid search over hyperparameters.

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.45]{figures/illustrations/avg_reward.eps}
\caption{Average normalized grasp quality versus iteration over 20 validation objects and 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net. We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation. We see that our algorithm converges faster with 10,000 models, never dropping below approximately 90\% of the grasp with highest $P_F$ from the 250 candidate set.}
\figlabel{avg-reward}
\vspace*{-15pt}
\end{figure}

\subsection{Sensitivity to Object Shape}
\seclabel{shape-sens}
To understand the behavior of Algorithm~\ref{alg:full} on individual 3D objects, we examined the convergnce rate with a 3D model of the only drill in Dex-Net and a spray bottle, which is an uncommon object category but has a few examples in Dex-Net.
~\figref{avg-reward-obj} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 4,000 iterations on these two objects.
We see that the spray bottle converges very quickly when using a prior dataset of 10,000 objects, finding the optimal grasp in the set in about 1,500 iterations.
\figref{spray-grasps} illustrates the grasps predicted to have the highest $P_F$ on the spray bottle by the different algorithms after 100 iterations.
However, performance on the drill does not increase using either 1,000 or 10,000 objects.

This suggests the value of the Dex-Net objects found by our shape similiarty MV-CNN, displayed in \figref{query}.
We see that the spray bottle has no nearest neighbors that are very close in shape in the 1,000 object dataset, but in the 10,000 object dataset two nearly identical spray bottles are retrieved.
On the other hand, the drill has no similar neighbors in either dataset, and the closest model in all of Dex-Net according to our similarity metric is a phone.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.31]{figures/illustrations/avg_reward_drill.eps}
\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net on a spray bottle (top) and drill (bottom). We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation. (Top) For the spray bottle, Algorithm~\ref{alg:full} does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimial grasp once 10,000 objects are used. (Bottom) The drill, which is relatively rare in the dataset, has no noticeable performance increase over Thompson sampling, even with 10,000 objects.}
\figlabel{avg-reward-obj}
\vspace*{-15pt}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.38]{figures/illustrations/nearest_neighbors.eps}
\caption{Illustration of the five nearest neighbor objects from Dex-Net to the spray bottle and drill using the multi-view CNN-based shape embedding and Euclidean distance for size 1,000 and 10,000 datasets from Dex-Net. We see that for the 1,000 object dataset neither model has relevant neighbors, while for the 10,000 object dataset two other spray bottles are returned. However, even with 10,000 objects no object geometrically similar to the drill is found. }
\figlabel{query}
\vspace*{-5pt}
\end{figure}

\section{Sensitivity to Similarity Kernel Bandwidth}
\seclabel{band-sens}
We also studied the sensitivity of our algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps}.
We varied the bandwidth of the kernel for the heightmap gradients to the higher value $1 / 350$ and the lower value $1 / 450$ , as this was the most discriminative feature maps found by our hyperparameter tuning.
\figref{bandwidth-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 20 validation objects.
We see that increasing the bandwidth of the kernel can reduce performance to be on par with uniform allocation.
This may be because overestimating similarities can lead to a grasp with high $P_F$ being predicted too low, or vice versa.
One the other hand, decreasing the bandwidth also decreases the convergence rate but Algorithm~\ref{alg:full} with 10,000 prior objects still outperforms Thompson sampling.
This suggests that a conservative setting of similiarity kernel bandwidth is important.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.23]{figures/illustrations/weight_sensitivity.eps}
\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right). (Left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation. (Bottom) A lower kernel bandwith decreases the convergence rate, but Algorithm~\ref{alg:full} still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.}
\figlabel{bandwidth-sens}
\vspace*{-10pt}
\end{figure}

\section{Sensitivity to Pose and Friction Uncertainty}
\seclabel{u-sens}
We also studied the sensitivity of our algorithm to the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
We tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
The uncertainty levels used to label grasps in Dex-Net were not changed.
\figref{u-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 45 test objects.
The normalized $P_F$ for increases and descreases across all methods for low and high uncertainty, respectively.
Also, prior data no longer increases convergence rate but a mismatch between the uncertainty on the test object and training objects does not cause performance to decrease below Thompson sampling without priors.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.23]{figures/illustrations/u_sensitivity.eps}
\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with low uncertainty (left) $\sigma_{t} = 0.0025, \sigma_{r} = 0.05, \sigma_{\gamma} = 0.05$ and high uncertainty (right) $\sigma_{t} = 0.01, \sigma_{r} = 0.2, \sigma_{\gamma} = 0.2$ on the test set. Lower uncertainty increases the quality for all methods and higher uncertainty decreases the quality for all methods. Interestingly, in both cases prior data has little effect but the convergence rate is still on par with Thompson sampling with no prior data.}
\figlabel{u-sens}
\vspace*{-10pt}
\end{figure}

>>>>

The bandwidths of our similarity kernel were constrained to be diagonal for the grasp parameters features $C_g = \Lambda$, isotropic for the global shape features $C_s = \sigma I$ for $\sigma \in \bR$, and a Gaussian mask $C_d$ centered on the differential heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
The bandwidths were selected by maximizing the log-likelihood of the true $P_F$ under the CCBP model~\cite{goetschalckx2011continuous} on the validation set using a grid search over hyperparameters.

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.40]{figures/illustrations/avg_reward.eps}
\caption{Average normalized grasp quality versus iteration over 20 validation objects and 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net. We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation. We see that our algorithm converges faster with 10,000 models, never dropping below approximately 90\% of the grasp with highest $P_F$ from the 250 candidate set.}
\figlabel{avg-reward}
\vspace*{-10pt}
\end{figure}

\subsection{Sensitivity to Object Shape}
\seclabel{shape-sens}
To understand the behavior of Algorithm~\ref{alg:full} on individual 3D objects, we examined the convergnce rate with a 3D model of a drill and spray bottle from the test set, both uncommon object categories in Dex-Net.
The bottom panel~\figref{avg-reward-obj} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 4,000 iterations on these two objects.
We see that the spray bottle converges very quickly when using a prior dataset of 10,000 objects, finding the optimal grasp in the set in about 1,500 iterations.
This convergence may be explained by the two similar spray bottles retrieved by our MV-CNN from the 10,000 object dataset.
\figref{spray-grasps} illustrates the grasps predicted to have the highest $P_F$ on the spray bottle by the different algorithms after 100 iterations.
However, performance on the drill does not increase using either 1,000 or 10,000 objects, as the closest model in all of Dex-Net according to our similarity metric is a phone.

%This suggests the value of the Dex-Net objects found by our shape similiarty MV-CNN, displayed in the top panel of \figref{query}.
%We see that the spray bottle has no nearest neighbors that are very close in shape in the 1,000 object dataset, but in the 10,000 object dataset two nearly identical spray bottles are retrieved.
%On the other hand, the drill has no similar neighbors in either dataset, and the closest model in all of Dex-Net according to our similarity metric is a phone.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.22]{figures/illustrations/avg_reward_w_neighbors.eps}
\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net and illustrations of five nearest neighbors in Dex-Net for a spray bottle (left) and drill (right). We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation. (Top-left) The spray bottle has no similar neighbors with 1,000 objects, but two other spray bottles are found by the MV-CNN in the 10,000 object set. (Bottom-left) As a result, the Dex-Net 1.0 algorithm does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimal grasp once 10,000 objects are used. (Top-right) The drill, which is relatively rare in the dataset, has not geometrically similar neighbors even with 10,000 objects. (Bottom-right) This leads to no noticeable performance increase over Thompson sampling.}
\figlabel{avg-reward-obj}
\vspace*{-15pt}
\end{figure}

@@

%\begin{figure}[t!]
%\centering
%\includegraphics[scale=0.38]{figures/illustrations/nearest_neighbors.eps}
%\caption{Illustration of the five nearest neighbor objects from Dex-Net to the spray bottle and drill using the multi-view CNN-based shape embedding and Euclidean distance for size 1,000 and 10,000 datasets from Dex-Net. We see that for the 1,000 object dataset neither model has relevant neighbors, while for the 10,000 object dataset two other spray bottles are returned. However, even with 10,000 objects no object geometrically similar to the drill is found. }
%\figlabel{query}
%\vspace*{-5pt}
%\end{figure}

\subsection{Sensitivity to Similarity, Pose and Friction Uncertainty}
\seclabel{band-sens}
We also studied the sensitivity of our algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps} and the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
We varied the bandwidth of the kernel for the heightmap gradients to the higher value $1 / 350$ and the lower value $1 / 450$, and tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
\figref{bnu-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 20 validation objects.
The results suggest that conservative setting of similiarity kernel bandwidth is important for convergence, and a mismatch between the the uncertainty levels for a test object and the labels in Dex-Net diminishes the effects of scaling with prior data.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.23]{figures/illustrations/combined_weight_and_u_sensitivity.eps}
\caption{Sensitivity to similiarity kernel (top) and pose and friction uncertainty (bottom) for the average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net.
with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
(Top-left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
(Top-right) A lower kernel bandwith decreases the convergence rate, but the Dex-Net Algorithm still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.
(Bottom-left) Lower uncertainty increases the quality for all methods and (bottom-right) higher uncertainty decreases the quality for all methods.
Interestingly, for variation in pose and friction uncertainty the convergence rate is still on par with Thompson sampling with no prior data.
}
\figlabel{bnu-sens}
\vspace*{-15pt}
\end{figure}

%\begin{figure}[t!]
%\centering
%\includegraphics[scale=0.23]{figures/illustrations/weight_sensitivity.eps}
%\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right). (Left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation. (Bottom) A lower kernel bandwith decreases the convergence rate, but Algorithm~\ref{alg:full} still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.}
%\figlabel{bandwidth-sens}
%\vspace*{-10pt}
%\end{figure}

%\subsection{Sensitivity to Pose and Friction Uncertainty}
%\seclabel{u-sens}
%We also studied the sensitivity of our algorithm to the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
%We tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
%The uncertainty levels used to label grasps in Dex-Net were not changed.
%\figref{u-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 45 test objects.
%The normalized $P_F$ for increases and descreases across all methods for low and high uncertainty, respectively.
%Also, prior data no longer increases convergence rate but a mismatch between the uncertainty on the test object and training objects does not cause performance to decrease below Thompson sampling without priors.

%\begin{figure}[t!]
%\centering
%\includegraphics[scale=0.23]{figures/illustrations/u_sensitivity.eps}
%\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with low uncertainty (left) $\sigma_{t} = 0.0025, \sigma_{r} = 0.05, \sigma_{\gamma} = 0.05$ and high uncertainty (right) $\sigma_{t} = 0.01, \sigma_{r} = 0.2, \sigma_{\gamma} = 0.2$ on the test set. Lower uncertainty increases the quality for all methods and higher uncertainty decreases the quality for all methods. Interestingly, in both cases prior data has little effect but the convergence rate is still on par with Thompson sampling with no prior data.}
%\figlabel{u-sens}
%\vspace*{-10pt}
%\end{figure}

### 2015-09-15 ICRA2016/bandits_docs/includes/introduction.tex
First 8 page version ready with fb from Mel and Mathieu as well

With ``Cloud Robotics and Automation," systems exchange data and perform computation via networks instead of operating in isolation with limited computation and memory.
Potential advantages to using the Cloud include Big Data, or access to updated libraries of images, maps, and object/product data, and Cloud Computing, or access to parallel grid computing for statistical analysis, machine learning, and planning.
Similar advantages have recently been used for vision and speech, where datasets with millions of examples such as ImageNet~\cite{deng2009imagenet} and the Fisher corpus~\cite{cieri2004fisher} have produced results~\cite{hannun2014deepspeech, hays2008im2gps, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods~\cite{kehoe2015survey}.
This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, environment configurations, etc.~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.085]{figures/dexnet_collage.jpg}
\caption{Sample of 3D mesh models from the Dex-Net dataset that currently includes over 10,000 models from the KIT object database~\cite{kasper2012kit}, the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, 3DNet\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison}. }
\figlabel{dexnet-teaser}
\vspace*{-15pt}
\end{figure}

Our primary contribution is a Multi-Armed Bandit (MAB) algorithm with correlated rewards to scale robust planning by learning from a large dataset of prior grasps and 3D object models.
Our algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.

To study scaling effects we develop Dex-Net 1.0, a growing dataset othat currently includes over 10,000 3D object models scaled to fit within a PR2 gripper and selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
%Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
%The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to approach larger scales.
Dex-Net also contains approximately 2.5 million parallel-jaw grasps, as each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
To the best of our knowledge, this is the largest dataset used for grasping research to-date.
We also incorporate multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects.

>>>>

Cloud-based Robotics and Automation systems exchange data and perform computation via networks instead of operating in isolation with limited computation and memory.
Potential advantages to using the Cloud include Big Data: access to updated libraries of images, maps, and object/product data; and Parallel Computation: access to parallel grid computing for statistical analysis, machine learning, and planning~\cite{kehoe2015survey}.
The advantages have recently been used in vision and speech, where datasets with millions of examples such as ImageNet have produced results~\cite{hannun2014deepspeech, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods.
This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, and environment configurations~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.08]{figures/dexnet_collage.jpg}
\caption{Sample of 3D mesh models from the Dex-Net dataset that currently includes over 10,000 models from the KIT object database~\cite{kasper2012kit}, the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, 3DNet\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20153d}, and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison}. }
\figlabel{dexnet-teaser}
\vspace*{-15pt}
\end{figure}

Our primary contribution is an algorithm based on a Multi-Armed Bandit (MAB) model with correlated rewards to speed up robust planning by learning from a large dataset of prior grasps and 3D object models.
Our algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.

To study scaling effects we developed Dex-Net 1.0, a growing dataset that currently includes over 10,000 3D object models scaled to fit within a PR2 gripper and selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
%Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
%The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to approach larger scales.
Dex-Net also contains approximately 2.5 million parallel-jaw grasps, as each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
To the best of our knowledge, this is the largest dataset used for grasping research to-date.
We also incorporate multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects.
